Exploratory_monthly

### 2023-02-09 code/analysis_code/exploratory_daily.qmd
Commented out Dr. Handel's code for manuscript
Now it can properly render Manuscript.qmd

Total Daily Vibrio
```{r}
daily %>% ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Daily Vibrio at all Sites") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend 
```

>>>>

Total Daily Vibrio
```{r}
tot_vib<- daily %>% ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Daily Vibrio at all Sites") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend

tot_vib
```
Save as PNG
```{r}
png(file = here("results", "plots", "tot_vib_allsites_daily.png"))
tot_vib
dev.off()
```

### 2023-02-09 code/analysis_code/exploratory_dust.qmd
Commented out Dr. Handel's code for manuscript
Now it can properly render Manuscript.qmd

Load Data
```{r}
dust_sum<-readRDS(file = here("data", "processed_data", "dust_sum.rds"))
```

Daily Dataframe
```{r}
daily_dust_sum<- dust_sum %>%
filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19')))
```

Plot Daily Dust Conc
```{r}
daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust)
)
```

Plot Total Dust Conc
```{r}
dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust)
)
```

>>>>

Load Data that has just DUST CONC
```{r}
dust_sum<-readRDS(file = here("data", "processed_data", "dust_sum.rds")) #Dataframe with copies_mL and dust concentration for 2022
dust_0 <- readRDS(here("data", "processed_data", "dust_0.rds"))
dust_6 <- readRDS(here("data", "processed_data", "dust_6.rds"))
dust_12 <- readRDS(here("data", "processed_data", "dust_12.rds"))
dust_18 <- readRDS(here("data", "processed_data", "dust_18.rds"))

```

Daily Dataframe with Sum dust
```{r}
daily_dust_sum<- dust_sum %>%
filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10
```

Plot Daily Dust Conc
```{r}
dust_sum_daily<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust))

dust_sum_daily
```

Plot Total Dust Conc
```{r}
dust_sum_2022<- dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust))

dust_sum_2022
```

Save as PNG
```{r}
png(file = here("results","plots", "dust_sum_daily.png"))
dust_sum_daily
dev.off()

png(file = here("results","plots", "dust_sum_2022.png"))
dust_sum_2022
dev.off()
```

### 2023-02-09 code/analysis_code/exploratory_monthly.qmd
Commented out Dr. Handel's code for manuscript
Now it can properly render Manuscript.qmd

Total Monthly Vibrio
```{r}
monthly %>% ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Monthly Vibrio at all Sites") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend 
```

>>>>

Total Monthly Vibrio
```{r}
tot_vib_allsites_monthly <- monthly %>% ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Monthly Vibrio at all Sites") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend

tot_vib_allsites_monthly
```
Save as PNG
```{r}
png(file = here("results","plots", "tot_vib_allsites_monthly.png"))
tot_vib_allsites_monthly
dev.off()
```
